---
title: "GoldenDeathX"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: spacelab    
---

```{r setup, include=TRUE}
library(data.table)
library(dplyr)
library(DT)
library(flexdashboard)
library(formattable)
library(PerformanceAnalytics)
library(plotly)
library(treemap)
knitr::opts_knit$set(root.dir = "..")
```

Boxplots {data-navmenu="Enrollment Summary"}
=====================================

Row {data-width=500}
-----------------------------------------------------------------------

### Performance Summary by Month

```{r echo=FALSE, Returns-Summary-Month}
spl_month_close <- readRDS("spl_month_close.rds")
charts.PerformanceSummary(
    ROC(spl_month_close, n = 1, type = "discrete"),
    main = "SPL Performance Summary"
)
```

Row {data-width=500}
-----------------------------------------------------------------------

### Yearly Returns

```{r echo=FALSE, Returns-Distribution-Yr}
spl_yearly <- readRDS("spl_yearly.rds")
plot_ly(spl_yearly, x = ~date, y = ~yearly.returns, type = 'bar', name = 'Returns by Year')
```

Charts {data-navmenu="Enrollment Summary"}
=====================================

Row {data-width=500}
-----------------------------------------------------------------------

### Return Distribution Golden Cross

```{r echo=FALSE, Boxplot-Distribution-GoldenDeathX}
returnsByCategory <- readRDS("returnsByCategory.rds")
chart.Boxplot(data.table(returnsByCategory) %>% select(starts_with("n")))
```

Column {data-width=350}
-----------------------------------------------------------------------

### Six Year Enrollment Trend

```{r echo=FALSE, include=TRUE, Total-Enrollment-Trends}

```

### Enrollment TYpe by Year

```{r}

```

### Current Year Enrollment Treemap

```{r}

```

Tables {data-navmenu="Enrollment Summary"}
=====================================  

Column
-------------------------------------
    
### Table 1
    
```{r}

```
   
Row
-------------------------------------
    
### Table 2
    
```{r}

```
    
### Table 3

```{r}

```

Length {data-navmenu="Institution Overview"}
=====================================

Row
-----------------------------------------------------------------------

### Program Length - 2 Year

```{r echo=FALSE, Length-Two-Yr}

```

Row
-----------------------------------------------------------------------

### Program Length - 4 Year

```{r echo=FALSE, Length-Four-Yr}

```

Type {data-navmenu="Institution Overview"}
=====================================  

Row
-------------------------------------
    
### Program Type - Independent
    
```{r echo=FALSE, Type-Independent}

```
   
Row
-------------------------------------
    
### Program Type - Public
    
```{r echo=FALSE, Type-Public}

```

Charts {data-navmenu="College Detail"}
=====================================     

Column {data-width=350}
-----------------------------------------------------------------------

### Cost of Attendance-Graduate Resident

```{r echo=FALSE, COA-Grad-Resident2}

```

### Cost of Attendance-Graduate Non Resident

```{r}

```

Tables {data-navmenu="College Detail"}
=====================================    

Row {data-width=450}
-------------------------------------
    
### Top 10 Institutions

```{r echo=FALSE, Top-10-Institutions}

```
    
### Bottom 10 Institutions

```{r echo=FALSE, Bottom-10-Institutions}

```

Row
-------------------------------------
    
### Institutional Ranking
    
```{r}

```

Page 1 {data-navmenu="Fin Aid Awd"}
=====================================    

Row
-------------------------------------
    
### Financial Aid Award-Undergraduate Resident

```{r echo=FALSE, Fin-Aid-Awd-Undergrad-Resident}

```
    
### Financial Aid Award Non Resident

```{r echo=FALSE, Fin-Aid-Awd-NonResident}

```

Column
-------------------------------------
    
### Financial Aid Award
    
```{r}

```

Page 2 {data-navmenu="Fin Aid Awd"}
=====================================    

Column 
-------------------------------------
    
### Chart 1
    
```{r}

```
   
Column {.tabset}
-------------------------------------
   
### Chart 2

```{r echo=FALSE, Fin-Aid-Awd2-Undergrad-Resident}

```
 
### Chart 3
    
```{r echo=FALSE, Fin-Aid-Awd2-NonResident}

```
