title: "GoldenDeathX"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: spacelab
--- 


```{r setup, echo=FALSE, include=FALSE}
knitr::opts_knit$set(root.dir = "..", echo = FALSE)
library(data.table)
library(dplyr)
library(DT)
library(dygraphs)
library(flexdashboard)
library(formattable)
library(highcharter)
library(hydroTSM)
library(PerformanceAnalytics)
library(plotly)
library(quantmod)
library(scales)
library(shiny)
library(shinydashboard)
library(tidyquant)
library(treemap)
library(xts)
library(zoo)
data("WorldPhones")
```

Boxplots {data-navmenu="Enrollment Summary"}
=====================================

Row {data-width=350}
-----------------------------------------------------------------------

### Number of Trade Days

```{r vbox-trade-days, eval=SPL.AX}
valueBox(paste(format(ndays(SPL.AX), big.mark = ","), "days"), caption = "# of Trade Days", icon="fa-pencil")
```

### Number of Calendar Days

```{r vbox-calendar-days, eval=SPL.AX}
valueBox(format(difftime(xts::last(SPL.AX), xts::first(SPL.AX)),big.mark=","), caption = "# of Calendar Days", icon="fa-pencil")
```


Row {data-width=500}
-----------------------------------------------------------------------

### Monthly Returns Summary

```{r Returns-Summary-Month, eval=spl_month_close}
charts.PerformanceSummary(
    ROC(spl_month_close, n = 1, type = "discrete"),
    main = "SPL Performance Summary"
    )
```

### Yearly Returns

```{r Returns-Distribution-Yr, eval=SPL.AX.yearly, include=TRUE}
plot_ly(SPL.AX.yearly, x = ~date, y = ~yearly.returns, type = 'bar', name = 'Returns by Year')
```

Row {data-width=500}
-----------------------------------------------------------------------

### Monthly Returns Table

```{r table-returns-monthly}
# datatable(retByMonth)
 ```

### Yearly Returns Table

```{r table-returns-yearly, eval=SPL.AX.yearly}
#knitr::kable(SPL.AX.yearly)
```

Charts {data-navmenu="Enrollment Summary"}
=====================================

Row {data-width=500}
-----------------------------------------------------------------------

### Return Distribution Golden Cross

```{r Boxplot-Distribution-GoldenDeathX}

```

Column {data-width=350}
-----------------------------------------------------------------------


### Current Year Enrollment Treemap

```{r}

```

Tables {data-navmenu="Enrollment Summary"}
=====================================  

Column
-------------------------------------
    
### Table 1
    
```{r}

```
   
Row
-------------------------------------
    
### Table 2
    
```{r}

```
    
### Table 3

```{r}

```

Length {data-navmenu="Institution Overview"}
=====================================

Row
-----------------------------------------------------------------------

### Program Length - 2 Year

```{r  Length-Two-Yr}

```

Row
-----------------------------------------------------------------------

### Program Length - 4 Year

```{r Length-Four-Yr}

```

Type {data-navmenu="Institution Overview"}
=====================================  

Row
-------------------------------------
    
### Program Type - Independent
    
```{r Type-Independent}

```
   
Row
-------------------------------------
    
### Program Type - Public
    
```{r Type-Public}

```

Charts {data-navmenu="College Detail"}
=====================================     

Column {data-width=350}
-----------------------------------------------------------------------

### Cost of Attendance-Graduate Resident

```{r COA-Grad-Resident2}

```

### Cost of Attendance-Graduate Non Resident

```{r}

```

Tables {data-navmenu="College Detail"}
=====================================    

Row {data-width=450}
-------------------------------------
    
### Top 10 Institutions

```{r Top-10-Institutions}

```
    
### Bottom 10 Institutions

```{r Bottom-10-Institutions}

```

Row
-------------------------------------
    
### Institutional Ranking
    
```{r}

```

Page 1 {data-navmenu="Fin Aid Awd"}
=====================================    

Row
-------------------------------------
    
### Financial Aid Award-Undergraduate Resident

```{r Fin-Aid-Awd-Undergrad-Resident}

```
    
### Financial Aid Award Non Resident

```{r Fin-Aid-Awd-NonResident}

```

Column
-------------------------------------
    
### Financial Aid Award
    
```{r}

```

Page 2 {data-navmenu="Fin Aid Awd"}
=====================================    

Column 
-------------------------------------
    
### Chart 1
    
```{r}

```
   
Column {.tabset}
-------------------------------------
   
### Chart 2

```{r Fin-Aid-Awd2-Undergrad-Resident}

```
 
### Chart 3
    
```{r Fin-Aid-Awd2-NonResident}

```
