---
title: "SPL Dashboard"
date: "`r params$reportdate`"
output:
  flexdashboard::flex_dashboard:
    orientation: row
    source_code: embed
    vertical_layout: fill
params:
  dateStart: "2002-01-02"
  dateEnd:  !r Sys.Date()
  dynamictitle: "My report"
  reportdate: !r Sys.Date()
  symbols: "SPL.AX"
  ticker: "SPL.AX"
runtime: shiny
theme: spacelab
---

```{r global, echo=FALSE, include=FALSE, message = FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
knitr::opts_knit$set(root.dir = "..", echo = FALSE)
library(d3heatmap)
library(data.table)
library(dplyr)
library(DT)
library(dygraphs)
library(flexdashboard)
library(formattable)
library(ggplot2)
library(gt)
library(here)
library(highcharter)
library(hydroTSM)
library(lubridate)
library(magrittr)
library(PerformanceAnalytics)
library(plotly)
library(quantmod)
library(readr)
library(rmarkdown)
library(scales)
library(shiny)
# library(shinybusy)
library(shinydashboard)
library(shinyWidgets)
# library(tidyquant)
library(tidyverse)
library(timetk)
library(treemap)
library(utils)
library(xts)
library(zoo)

```

```{r functions}

# A function to build an xts object to hold both ticker returns.
# Function to calculate monthly returns on a stock
monthly_stock_returns <- function(ticker, dateStart) {
  
  # Download the data from Yahoo finance
  symbol <- getSymbols("SPL.AX", src = 'yahoo', from = "2019-07-02",
                       auto.assign = FALSE, warnings = FALSE)
  
  # Transform it to monthly returns using the periodReturn function from quantmod
  data <- periodReturn("SPL.AX", period = 'monthly', type = 'log')

  # Let's rename the column of returns to something intuitive because the column
  # name is what will eventually be displayed on the time series graph
  colnames(data) <- as.character("SPL.AX")

  # We want to be able to work with the xts objects that result from this function
  # so let's explicitly put them to the global environment with an easy to use
  # name, the stock ticker
  assign("SPL_returns", data, .GlobalEnv)
} # monthly_stock_returns


# xts_price <- tk_xts(price())
# xts_ma <- tk_xts(ma_SPL)
# merge(xts_price,xts_ma, join='inner')[,c(6:10)]
# xts.obj[paste(start.date,end.date,sep="::")]
# merge(xts_price, xts_ma, join = 'inner')[,c(6:10)][paste(format(input$dateRange[1]),format(input$dateRange[2]),sep="::")] 

xprices <- function() {

  symbols <- ("^IRX")
  
  tq_get(symbols,
         get = "stock.prices",
         from = input$dateRange[1],
         to = input$dateRange[2])
    
}
```

```{r rdsInput}
calendarDays <- readRDS(here::here("rds","calendarDays.rds"))
dtEMA  <- readRDS(here::here("rds","dtEMA.rds"))
golden <- readRDS(here::here("rds","golden.rds"))
ma_SPL <- readRDS(here::here("rds","ma_SPL.rds"))
returnsByCategory <- readRDS(here::here("rds","returnsByCategory.rds"))
tradeDays <- readRDS(here::here("rds","tradeDays.rds"))
trend  <-  data.table(readRDS(here::here("rds","trend.rds")))
xtsEMA <- readRDS(here::here("rds","xtsEMA.rds"))
```

1.1 Summary {data-navmenu="1-Performance" data-icon="fa-list" data-orientation=rows}
=====================================  

Input {.sidebar}
-------------------------------------
  
```{r 1.0.0.1-sidebarInput}

dateRangeInput("dateRange",
               "Historical data",
               start = params$dateStart,
               end   = Sys.Date())

# actionButton("go", "Submit")

```

```{r 1.0.0.1-sidebar-ActionGo}

tqPrices <- eventReactive(input$go, {
  
  tqPrices <- tq_get("SPL.AX", 
              get = "stock.prices",
              from = format(input$dateRange[1]),
              to = format(input$dateRange[2])) 
})


#  date        open  high   low close volume adjusted   change
price <- reactive({
  tq_get("SPL.AX", from = format(input$dateRange[1]), to = format(input$dateRange[2])) %>%
        mutate(change = close - open,
          ema020 = EMA(na.fill0(close,0),20),
          ema050 = EMA(na.fill0(close,0),50),
          ema100 = EMA(na.fill0(close,0),100),
          ema200 = EMA(na.fill0(close,0),200),
          sma020 = SMA(na.fill0(close,0),20),
          sma050 = SMA(na.fill0(close,0),50),
          sma100 = SMA(na.fill0(close,0),100),
          sma200 = SMA(na.fill0(close,0),200)
          )
})

```

Column {data-height=60}
-------------------------------------

###

```{r 1.1.1.1-vbox-calendar-days}

flexdashboard::renderValueBox({
  xts_price <- tk_xts(price())
  calendarDays <- format(end(xts_price)-start(xts_price), big.mark = ",")
  calendarDays <- substr(calendarDays, 1, nchar(calendarDays)-5)
  
  flexdashboard::valueBox(
      paste(calendarDays, "", " Calendar Days")
      ,color = #0000ff
      ,icon = "fa-calendar"
  )
})

```

###

```{r 1.1.1.2-vbox-returns-roi}

flexdashboard::renderValueBox({
  xts_price <- tk_xts(price())
  cumReturn <- percent((as.numeric(last(xts_price[,4])) - as.numeric(first(xts_price[,4]))) / (as.numeric(first(xts_price[,4]))))

  flexdashboard::valueBox(
      paste(as.character(cumReturn), "", " ROI")
      ,color = ifelse(cumReturn > 0, "teal", "red")
      ,icon = 'ion-cash'
  )
})

```

###

```{r 1.1.1.3-vbox-returns-annualized}

flexdashboard::renderValueBox({
  xts_price <- tk_xts(price())
  annReturn <- percent((as.numeric(last(xts_price[,4])) / as.numeric(first(xts_price[,4]))) ^ ((1/nyears(xts_price)))-1)

  flexdashboard::valueBox(
      paste(as.character(annReturn), "", " Annualized Return")
      ,color = ifelse(annReturn > 0, "teal", "red")
      ,icon = 'ion-cash'
  )
})

```

###

```{r 1.1.1.4-vbox-trade-days}

flexdashboard::renderValueBox({
  xts_price <- tk_xts(price())
  tradeDays <- format(ndays(xts_price), big.mark = ",")

  flexdashboard::valueBox(
      paste(tradeDays, "", " Trade Days")
      ,color = #0000ff
      ,icon = "fa-calendar"
  )
})

```

Row {data-height=200}
-------------------------------------

### Stock Price Table

```{r 1.1.2.1-table-Price}
DT::renderDataTable({
  DT::datatable(price(), rownames = FALSE, 
    options = list(pageLength = 20, order = list(list(0, 'desc')))) %>% 
    formatCurrency(c('open', 'high', 'low', 'close', 'adjusted', 'change', 
                     'ema020', 'ema050', 'ema100', 'ema200', 'sma020', 'sma050', 'sma100', 'sma200')) %>% 
    formatDate(c('date')) %>%
    formatStyle('volume', 
      background = styleColorBar(price()$volume, 'steelblue')
    ) %>% 
    formatStyle(
      'change', 
      color = styleInterval(c(0), c('maroon', 'darkgreen'))
    )  
})
```

Row {data-height=200}
-------------------------------------

### Stock Price Over Time (Chart)
```{r  1.1.3.1-viz-Price, eval=price}
# y <- getSymbols("CSL.AX", auto.assign = FALSE)


renderHighchart({
  xts_price <- tk_xts(price())
  colnames(xts_price) <- paste0(input$ticker,'.', colnames(xts_price))
  highchart(type = "stock") %>% 
    hc_add_series(xts_price, type = "candlestick")
#    hc_add_series(RSI.BuyLevel, color = hex_to_rgba("blue", 0.7),
#                yAxis = 2, name = "Buy level") 
#    hc_add_series(y, type = "ohlc")
})

```


### Distribution

```{r 1.1.3.2-viz-histogram, eval=price}

# draw a histogram
renderPlot({

    # generate bins based on input$bins from ui.R
    x <- tk_xts(price())
    hist(x[,6]
         ,main="Closing Price"
         ,xlab="price"
         ,ylab="Count"
         ,col="darkmagenta"
         ,freq=TRUE
         ,border='white'
         ,xlim=c(0.0,2)
         ,seq(0.1,2, by = 0.10))
  })
```

1.2 Returns {data-navmenu="1-Performance" data-icon="ion-cash"}
=====================================

Column {data-width=500 .tabset .tabset-fade}
-------------------------------------

### Daily Returns

```{r 1.2.1.a-viz-ret-Daily, eval=price}

renderHighchart({
  xts_price <- tk_xts(price())
  dailyRet<-periodReturn(xts_price[,6], period = 'daily') * 100
#  colnames(xts_price) <- paste0(input$ticker,'.', colnames(xts_price))
  highchart(type = "stock") %>% 
    hc_add_series(dailyRet, type = "column")
})
``` 

### Weekly Returns

```{r 1.2.1.b-viz-ret-Weekly, eval=price}

renderHighchart({
  xts_price <- tk_xts(price())
  weeklyRet<-periodReturn(xts_price[,6], period = 'weekly') * 100
#  colnames(xts_price) <- paste0(input$ticker,'.', colnames(xts_price))
  highchart(type = "stock") %>% 
    hc_add_series(weeklyRet, type = "column")
})

``` 

### Monthly Returns

```{r 1.2.1.c-viz-ret-monthly, eval=price}

renderHighchart({
  xts_price <- tk_xts(price())
  monthlyRet<-periodReturn(xts_price[,6], period = 'monthly') * 100
#  colnames(xts_price) <- paste0(input$ticker,'.', colnames(xts_price))
  highchart(type = "stock") %>% 
    hc_add_series(monthlyRet, type = "column")
})

``` 

### Quarterly Returns

```{r 1.2.1.d-viz-ret-quarterly, eval=price}

renderHighchart({
  xts_price <- tk_xts(price())
  quarterlyRet<-periodReturn(xts_price[,6], period = 'quarterly') * 100
#  colnames(xts_price) <- paste0(input$ticker,'.', colnames(xts_price))
  highchart(type = "stock") %>% 
    hc_add_series(quarterlyRet, type = "column")
})

```  

### Annual Returns

```{r 1.2.1.e-viz-ret-annual, eval=price}

renderHighchart({
  xts_price <- tk_xts(price())
  annualRet<-periodReturn(xts_price[,6], period = 'yearly') * 100
#  colnames(xts_price) <- paste0(input$ticker,'.', colnames(xts_price))
  highchart(type = "stock") %>% 
    hc_add_series(annualRet, type = "column")
})

```

### Future Returns

```{r 1.2.1.f-viz-ret-future, eval=price}

renderHighchart({
  xts_price <- tk_xts(price())
  dailyRet<- periodReturn(xts_price[,6], period = 'daily')
  dailyRet[dailyRet==0]<- NA
  dailyRet <- 1 + dailyRet
  fv <- cumprod(na.omit(dailyRet))
  highchart(type = "stock") %>% 
  hc_add_series(fv, type = "line") %>%
  hc_add_theme(hc_theme_darkunica()) %>%
  hc_yAxis(title = list(text = "$1"),
         opposite = TRUE,
         plotLines = list(
           list(label = list(text = "This is a plotLine"),
                color = "blue",
                width = 3,
                value = 1.0)))
})

```


2.1 Summary {data-navmenu="2-Trends" data-icon="fa-list"}
=====================================
 
Column {data-width=500 .tabset .tabset-fade}
-------------------------------------

### Trend Summary Table A

```{r 2.1.1.a-table-Trend}

DT::renderDataTable({
  DT::datatable(trend, rownames = FALSE, 
    options = list(pageLength = 10, order = list(list(0, 'desc')))) %>%
    formatDate(c('startDate', 'endDate')) %>%
    formatRound('count', 0) %>%
    formatPercentage('return')  %>%
    formatStyle('return', 
      background = styleColorBar(range(trend$return), 'lime'))%>%
    formatStyle('count', 
      color = styleInterval(c(0), c('maroon', 'darkgreen'))
    )  
})

```


### Trend Summary Table B

```{r 2.1.1.b-viz-ret-quarterly, eval=price}

renderHighchart({
  xts_price <- tk_xts(price())
  quarterlyRet<-periodReturn(xts_price[,6], period = 'quarterly') * 100
#  colnames(xts_price) <- paste0(input$ticker,'.', colnames(xts_price))
  highchart(type = "stock") %>% 
    hc_add_series(quarterlyRet, type = "column")
})

```

Row {data-height=250}
-------------------------------------

### Trend Over Time (Chart)
```{r  2.1.2.1-viz-Trend, eval=xtsEMA}

```

2.2 Golden Cross {data-navmenu="2-Trends" data-icon="fa-list" data-orientation=rows}
=====================================

Input {.sidebar}
-------------------------------------
  
```{r 2.2.0.1-sidebar-Input-golden}

dateRangeInput("dateRange",
               "Historical data",
               start = params$dateStart,
               end   = Sys.Date())

actionButton("go", "Submit")

```

```{r 2.2.0.1-sidebar-ActionGo-golden}
# We will use this in the table after the submit button is activated

prices <- eventReactive(input$go, {

  prices <- 
    getSymbols("SPL.AX", src = 'yahoo'
               ,from = format(input$dateRange[1])
               ,to = format(input$dateRange[2])
               ,auto.assign = TRUE
               ,warnings = FALSE) %>% 
    map(~Cl(get(.))) %>% 
    reduce(merge)

})
```

Row {data-height=260}
-------------------------------------

###

```{r  2.2.1.1-table-golden-drawdown}
maxDrawdown(tk_xts(golden))
```

```{r 2.2.2.1-table-golden-returns}
table.AnnualizedReturns(tk_xts(golden),Rf=0.02/252)
```

Row
-------------------------------------

### Golden Cross Performance Summary

```{r r 2.2.3.1-viz-golden-performance}

renderPlot({
    charts.PerformanceSummary(
      tk_xts(golden)[paste(format(input$dateRange[1]),format(input$dateRange[2]),sep="::")]
      ,Rf = 0.02
      ,main = "Golden Cross Performance Summary"
      ,geometric = FALSE
      ,colorset=rainbow12equal
    )
})  
```

Column {data-width=500 .tabset .tabset-fade}
-------------------------------------

### Golden Cross Returns

```{r 2.2.4.a-table-golden-returns}
  renderTable(price(), striped = TRUE, rownames = TRUE)
```


### Stock Price Table

```{r 2.2.4.b-table-golden-price}
DT::renderDataTable({
  DT::datatable(price(), rownames = FALSE, 
    options = list(pageLength = 20, order = list(list(0, 'desc')))) %>% 
    formatCurrency(c('open', 'high', 'low', 'close', 'adjusted', 'change')) %>% 
    formatDate(c('date')) %>%
    formatStyle('volume', 
      background = styleColorBar(price()$volume, 'steelblue')
    ) %>% 
    formatStyle(
      'change', 
      color = styleInterval(c(0), c('maroon', 'darkgreen'))
    )  
})
```


### Golden Cross Performance Summary Table

```{r 2.2.4.c-table-golden-performance}
DT::renderDataTable({
  DT::datatable(price(), rownames = FALSE, 
    options = list(pageLength = 20, order = list(list(0, 'desc')))) %>% 
    formatCurrency(c('open', 'high', 'low', 'close', 'adjusted', 'change')) %>% 
    formatDate(c('date')) %>%
    formatStyle('volume', 
      background = styleColorBar(price()$volume, 'steelblue')
    ) %>% 
    formatStyle(
      'change', 
      color = styleInterval(c(0), c('maroon', 'darkgreen'))
    )  
})
```


### Miscellaneous Table

```{r 2.2.4.d-table-golden-misc}
DT::renderDataTable({
  DT::datatable(price(), rownames = FALSE, 
    options = list(pageLength = 20, order = list(list(0, 'desc')))) %>% 
    formatCurrency(c('open', 'high', 'low', 'close', 'adjusted', 'change')) %>% 
    formatDate(c('date')) %>%
    formatStyle('volume', 
      background = styleColorBar(price()$volume, 'steelblue')
    ) %>% 
    formatStyle(
      'change', 
      color = styleInterval(c(0), c('maroon', 'darkgreen'))
    )  
})
```


### Table 5

```{r 2.2.4.e-table-golden-five}

```

2.3 Death Cross {data-navmenu="2-Trends" data-icon="fa-list" data-orientation=rows}
=====================================

```{r 2.3.1.1-xxx-death}
 
```

2.4 No Cross {data-navmenu="2-Trends" data-icon="fa-list" data-orientation=rows}
=====================================

```{r 2.4.1.1-xxx-neither}
 
```

3.1 Summary {data-navmenu="3-TechnicalAnalysis" data-icon="fa-list" data-orientation=rows}
=====================================

Input {.sidebar}
-------------------------------------
  
```{r 3.1.0.1-sidebar-ActionGo-TA}

dateRangeInput("dateRange3",
               "Historical data",
               start = params$dateStart,
               end   = Sys.Date())

```

Column {}
-------------------------------------

### Gauge 3.1.1.1
    
```{r 3.1.1.1-vbox-gauge}
flexdashboard::renderGauge({
    gauge(60, min = 0, max = 100, symbol = "%") 
  })
```

### Gauge 3.1.1.2
    
```{r 3.1.1.2-vbox-gauge}
flexdashboard::renderGauge({
    gauge(60, min = 0, max = 100, symbol = "%") 
  })
```


### Gauge 3.1.1.3
    
```{r 3.1.1.3-vbox-gauge}
flexdashboard::renderGauge({
  xts_price <- tk_xts(price())
  cumReturn <- (as.numeric(last(xts_price[,4])) - as.numeric(first(xts_price[,4]))) / (as.numeric(first(xts_price[,4])))
  
    gauge(cumReturn*100, min = -100, max = 100, symbol = "%") 
  })
```

Column {}
-------------------------------------
### Stock Price Table

```{r 3.1.2.1-table-price}
DT::renderDataTable({
  DT::datatable(price(), rownames = FALSE, 
    options = list(pageLength = 20, order = list(list(0, 'desc')))) %>% 
    formatCurrency(c('open', 'high', 'low', 'close', 'adjusted', 'change')) %>% 
    formatDate(c('date')) %>%
    formatStyle('volume', 
      background = styleColorBar(price()$volume, 'steelblue')
    ) %>% 
    formatStyle(
      'change', 
      color = styleInterval(c(0), c('maroon', 'darkgreen'))
    )  
})
```

Column {.tabset .tabset-fade}
-------------------------------------
### Time Series
```{r 3.1.3.a-viz-time-series, eval=prices}
  renderPlot({
  xts_price <- tk_xts(price())
  chartSeries(xts_price, theme = chartTheme("black"),TA="addCMF()")
               
})
```  

### Time Series 2
```{r 3.1.3.b-viz-time-series, eval=prices}
  renderPlot({
  xts_price <- tk_xts(price())
  chartSeries(xts_price, theme = chartTheme("white"),TA="addMACD()")
               
})
```

### Time Series 3

```{r 3.1.3.c-viz-time-series, eval=xtsEMA}
  renderPlot({
  chartSeries(xtsEMA[,2]
              ,theme = chartTheme("black")
              ,TA=c(
                addVo()
                ,addBBands()
                ,addEMA(n=10, col = "blue")
                ))
})

```

4.1 Summary {data-navmenu="4-Forecast" data-icon="fa-list" data-orientation=rows}
=====================================

Column {.tabset .tabset-fade}
-------------------------------------

### Forecast Column1a

```{r 4.1.1.1-xxx}

```

Column
-------------------------------------

### Forecast Column2a

```{r 4.1.2.1-xxx}

```

5.1 Summary {data-navmenu="5-BackTesting" data-icon="fa-list" data-orientation=rows}
==========================================

Column {data-width=500 .tabset .tabset-fade}
-------------------------------------

### BackTesting01a

```{r  5.1.1.1-table-ema, eval=price}
  xtsEMA<-tk_xts(xtsEMA)
  xtsEMA
```

5.2 Detail {data-navmenu="5-BackTesting" data-icon="fa-list" data-orientation=rows}
==========================================

Column {data-width=500 .tabset .tabset-fade}
-------------------------------------

### Distribution 2

```{r 5.2.1.2-xxx, eval=price}
renderHighchart({

    # generate bins based on input$bins from ui.R
    x <- tk_xts(price())
    hist(x[,6],  col="darkmagenta", freq=FALSE, border='white', xlim=c(0,2))

  })
```

6.1 Summary {data-navmenu="6-WordCloud" data-icon="fa-list" data-orientation=rows}
=====================================

Column {data-width=500 .tabset .tabset-fade}
-------------------------------------

### WordCloud01a

```{r 6.1.1.1-table-ret-category wordCloud01a}
returnsByCategory
```

6.2 Detail {data-navmenu="6-WordCloud" data-icon="fa-list" data-orientation=rows}
=====================================

Column {data-width=500 .tabset .tabset-fade}
-------------------------------------

### WordCloud02a

```{r 6.2.1.a-table-dtEMA, eval=dtEMA}
dtEMA
```

### WordCloud02b

```{r 6.2.1.b-table-dtEMA, eval=trend}
trend
```
